\Huge Don't interpolate your data!

### 2022-11-02 paper/main.tex
add bit-flag mask concept and minor edits to other assumptions

@@

\paragraph{Multi-epoch spectra with shifts}
We will assume that there are $n$ observations (epochs) of the same star (or maybe of different stars or quasars, say, that are assumed to be more-or-less identical, intrinsically, but let's think of a single star for now).
Each of these observations $i$ (with $1\leq i\leq n$) produces a one-dimensional observed (noisy) image $y_i$.
The $y_i$ can be thought of as $m_i$-vectors in what follows, where $m_i$ is the number of pixels in the spectrum.
The different observations are made at different relative velocities (star minus spectrograph) such that the different images are shifted by a different shift $\Delta x_i$ relative to the detector or extracted wavelength grid.

\paragraph{Shift operators}
Because the shifts might be non-linear, the shifts $\Delta x_i$ won't be pure numbers but something more like shift operators.
That is, if there were a true spectrum $\tilde{y}$, each individual noisy image $y_i$ would be related to that true spectrum by a shift operator acting on that true spectrum, plus noise.
We will begin by assuming that (from some external information) we know these shift operators very accurately.
At the end we may (do we?) return to the question of how those shift operators are determined.

@@

>>>>

% notes

@@

\paragraph{Multi-epoch spectra with shifts}
We will assume that there are $n$ observations (epochs) of the same star (or maybe of different stars or quasars, say, that are assumed to be more-or-less identical, intrinsically, but let's think of a single star for now).
Each of these observations $i$ (with $1\leq i\leq n$) produces a one-dimensional observed (noisy) image $y_i$.
The $y_i$ can be thought of as $m_i$-vectors in what follows, where $m_i$ is the number of pixels in the $i$-th spectrum.
The different observations are made at different relative velocities (star minus spectrograph) such that the different images are shifted by a different shift $\Delta x_i$ relative to the detector or extracted wavelength grid.

\paragraph{Shift operators}
Because the shifts might be non-linear, the shifts $\Delta x_i$ won't be pure numbers but something more like shift operators.
That is, if there were a true spectrum $\tilde{y}$, each individual noisy image $y_i$ would be related to that true spectrum by a shift operator acting on that true spectrum, plus noise.
We will begin by assuming that (from some external information) we know these shift operators very accurately.
At the end we may (do we?) return to the question of how those shift operators are determined. ANDY: SMASH! Out of scope!

@@

\paragraph{Bit-flag masks (or is it bit-masks? bit-pixel masks?)}
A bit-flag mask is often used to encode meta data about an observation that otherwise cannot be represented by the spectrum $y_i$ or its asssociated variance tensor $C_i$ (e.g., poorly described line spread function), and we often want to propagate this meta data to appropriate pixels in the combined spectrum.
These bit-flag masks are usually encoded as integers with up to $p$ potential flags, allowing for multiple flags to be encoded as a single value $\sum^{P}_{p=0} 2^p$. 
This bit-flag mask can be separated into $p$ masks where each has value 1 in the locations where the flag is marked, and 0 in the locations where it is not.
